%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3}  & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEduheading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3}  & \text{\small #4} \\
      \text{\small #5}  & \textit{\small} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}    

\begin{center}
    \textbf{\Huge \scshape  MADHAV KUMAR } 
    \\ \vspace{10pt}
    \href{https://github.com/madhav-mknc}{\underline{madhav} \faGithub} $|$
    \href{https://www.linkedin.com/in/madhav-kumar-030785205/}{\underline{madhav} \faLinkedin} $|$
    \href{https://madhav-mknc.github.io/portfolio/}{\underline{madhav} \Mundus} $|$
   \href{https://twitter.com/5mknc5/}{\underline{5mknc5}} {$X$} $|$
    \small Undergrad, IIT Delhi
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEduheading
      {Indian Institute of Technology Delhi}{New Delhi, Delhi}
      {B.Tech. - Major in Engineering Physics, Minor in Computer Science and Engineering}
      {2020 -- Present}
      {}

    \resumeEduheading
      {Coast Guard Public School}{Daman}
      {High School}
      {2020}
      {}

    % \resumeEduheading
    %   {Kendriya Vidyalaya Sangathan}{Visakhapatnam}
    %   {Class X CBSE}{2018}
    %   {}

  \resumeSubHeadingListEnd



% \section{Awards and Honours}
%  \begin{itemize}[leftmargin=0.15in]
%     \itemsep0em
%     \small{\item{
%      Qualified the \textbf{JEE Advanced 2020} examination amongst 245,000 candidates \\
%     }}
%     \small{\item{
%      Qualified the \textbf{JEE Main 2020} examination amongst 1.1 million candidates \\
%     }}
%     % \small{\item{
%     %  Current rating of \textbf{1294} on Codeforces. (Handle: {\texttt{\href{http://codeforces.com/profile/A9_10}{A9\_10}}})  \\
%     % }}
    
%  \end{itemize}



%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {X-Hall: Chatroom}{Feb-April 2023}
      {}{\texttt{\href{https://github.com/madhav-mknc/x-hall}{github.com/madhav-mknc/x-hall}}}
      \resumeItemListStart
        \resumeItem{Used \textbf{TCP Sockets} in Python for creating a network infrastructure.}
        \resumeItem{Used \textbf{Multi-threading} for achieving the concurrency in the program.}
        \resumeItem{Implemented \textbf{P2P Networking}; Command Line Interface.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Links Crawler}{January 2022}
      {}{\texttt{\href{https://github.com/madhav-mknc/links-crawler}{github.com/madhav-mknc/links-crawler}}}
      \resumeItemListStart
        \resumeItem{A \textbf{Web Crawler} that fetches all the URL links found on a given URL and then recursively scrapes all the data.}
        \resumeItem{It was initially created for collecting data for training \textbf{ML models}.}
        \resumeItem{Used \textbf{requests} and \textbf{BeautifulSoup} libraries of Python.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Delta (Voice of LLM)}{May-June 2023}
      {}{\texttt{\href{https://github.com/madhav-mknc/delta-LLM}{github.com/madhav-mknc/delta-LLM}}}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{Virtual Assistant} to convert a spoken command to text using \textbf{Google-translate API} package for interacting with the \textbf{LLM models} like OpenAI's GPT3/3.5/4 models.}
        \resumeItem{Written in Python and used the \textbf{LangChain} framework and the \textbf{Hugging face APIs}.}
      \resumeItemListEnd

    \resumeSubheading
      {Network Crawler}{December 2022}
      {}{\texttt{\href{https://github.com/madhav-mknc/network-crawler}{github.com/madhav-mknc/network-crawler}}}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{host discovery} program which when provided a Network Address can crawl the whole network and Scan for the active hosts in the network.}
        \resumeItem{Used \textbf{Socket} Library in Python and also Implemented \textbf{Scapy} framework for an alternative version.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Who-Is-Online}{Mar-present 2023}
      {}{\texttt{\href{https://github.com/madhav-mknc/who-is-online}{github.com/madhav-mknc/who-is-online}}}
      \resumeItemListStart
        \resumeItem{Built a \textbf{chrome extension} that aims to create a hub for chrome users where users can interact with the other users accessing the same site as them, and can also join a mapped discord server/channel directly.}
        \resumeItem{Written in Javascript and Python, used Python \textbf{Discord API} and \textbf{Flask}.}
      \resumeItemListEnd

    \resumeSubheading
      {Eye-PERS}{May 2023}
      {}{\texttt{\href{https://github.com/madhav-mknc/eye-pers}{github.com/madhav-mknc/eye-pers}}}
      \resumeItemListStart
        \resumeItem{Created a recommendation engine for eyewear on Lenskart: Improved Personalized Eyewear Recommendation System (Eye-PERS)}
        \resumeItem{Built with \textbf{Object Detection}, \textbf{Haarcascades}, \textbf{Image processing} (and other ML technologies), \textbf{AWS Rekognition} (API).}
      \resumeItemListEnd
     
    \resumeSubheading
      {Github-GPT}{June 2023}
      {}{\texttt{\href{https://github.com/Madhav-MKNC/githubGPT}{github.com/Madhav-MKNC/githubGPT}}}
      \resumeItemListStart
        \resumeItem{Developed a Command Line-based bot that scans the source code of a provided Github repository and automatically raises issues if found. An advanced version of this also fixes the issues and submits a Pull Request.}
        \resumeItem{Written in Python and used \textbf{LangChain} framework and \textbf{LLM models} for detecting issues and code generation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\newpage

%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages: }{Python, Java, C, C++, bash/batch/powershell scripting, GoLang, HTML/CSS, etc.} \\
     \textbf{Libraries: }{Flask, Langchain, Llama\_index, Socket, BeautifulSoup, Selenium, Scrapy, Scapy, NMAP, NumPy, etc.} \\
     \textbf{Tools/Utilities: }{Git, MySQL, Linux, Burpsuit, Metasploit, Wireshark, Ngrok, Virtual Machines, Hashcat, Hydra, etc.} \\
     \textbf{Experience in: }{Web Scraping, Object Oriented Programming Systems, Data Structures and Algorithms, Capture the Flags (CTFs), Generative AI, Decentralization, Web Development, CLI developement, Open Source Development etc.} \\
     \textbf{Achievements: }{
    \textit{5-Star} rated in C++, Python, Problem Solving and Java on HackerRank.
    \textit{3-Star} rated on \textit{Codechef} with a rating of more than \textit{1700}. \textit{Codeforces} rating \textit{1294}. More than two years’ of Experience in using Linux/Unix (Ubuntu, Kali Linux, Parrot OS, Tail-OS), learnt Computer Networking (Implemented using Python)
     } \\
    }}
 \end{itemize}
 
 \section{Relevant Courses}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Data Structures and Algorithms, Computer Networks, Discrete Mathematical Structures, Penetration Testing, Command Line Interfaces, Networking in python, Intro to Blockchain, Computational physics, Signals and Systems, etc.
    }}\\
 \end{itemize}
 


%-------------------------------------------
\end{document}
